Improved Hydrodynamic/Reaction Coupling for Flows With Nuclear Statistical Equilibrium

### 2020-10-29 simplified_sdc_intro/paper.tex
minor comments

The NSE table requires:
\begin{equation}
  \label{eq:aux:ye}
  Y_e = \sum_k \frac{Z_k X_k}{A_k}
\end{equation}
(where $A_k$ and $Z_k$ are the atomic weight and atomic number of nucleus $k$) and provides
\begin{align}
\label{eq:aux:abar}
\bar{A} &= \left [ \sum_k \frac{X_k}{A_k} \right ]^{-1} \\
\label{eq:aux:bea}
\left (\frac{B}{A} \right ) &= \sum_k \frac{B_k X_k}{A_k}
\end{align}
where $B_k$ is the binding energy of nucleus $k$.  In our simulations,
we store these 3 quantities as auxiliary data that is carried along
with the rest of the fluid state in each zone.  The table also returns
values of the mass fractions mapped onto the 19-isotopes we carry, $X_k$, and the time-derivative of $Y_e$, $dY_e/dt$.
We'll use the notation:
\begin{equation}
\nse{\rho,T,Y_e} \rightarrow \bar{A}, X_k, (B/A), dY_e/dt
\end{equation}
to represent the NSE table call and its inputs and outputs.

@@

The compositional quantities
it carries, $\bar{A}$ and $Y_e$ are not representable from the 19
isotopes we carry in the main network. For this reason, when we are
using the NSE network, we always take the composition quantities in
the EOS directly from the auxiliary state in each zone instead of
using the $X_k$ directly. Our equation of state needs $\bar{Z}$ in addition
to the auxiliary quantities, which is is easily computed as
\begin{equation}
\bar{Z} = \bar{A} Y_e
\end{equation}

@@

We initializing the mass fractions, $X_k$, and then compute the
electron fraction, $Y_e$, from them.  For the two other composition
quantities we carry, $\bar{A}$, and $(B/A)$, we need values that are
consistent with the value of $Y_e$ and the nuclei stored in the NSE
table.  Therefore, if the thermodynamic conditions put us in NSE
(using the conditions defined below), then we get $\bar{A}$ and
$(B/A)$ from the NSE table.  Otherwise, we compute these directly from
$X_k$.

>>>>

The NSE table requires:
\begin{equation}
  \label{eq:aux:ye}
  Y_e = \sum_k \frac{Z_k X_k}{A_k}
\end{equation}
(where $A_k$ and $Z_k$ are the atomic weight and atomic number of nucleus $k$) and provides
\begin{align}
\label{eq:aux:abar}
\bar{A} &= \left [ \sum_k \frac{X_k}{A_k} \right ]^{-1} \\
\label{eq:aux:bea}
\left (\frac{B}{A} \right ) &= \sum_k \frac{B_k X_k}{A_k}
\end{align}
where $B_k$ is the binding energy of nucleus $k$.  In our simulations,
we store these 3 quantities as auxiliary data that is carried along
with the rest of the fluid state in each zone.  The table also returns
values of the mass fractions mapped onto the 19-isotopes we carry, $X_k$, and the time-derivative of $Y_e$, $dY_e/dt$.
We use the notation:
\begin{equation}
\nse{\rho,T,Y_e} \rightarrow \bar{A}, X_k, (B/A), dY_e/dt
\end{equation}
to represent the NSE table call and its inputs and outputs.

@@

The compositional quantities
it carries, $\bar{A}$ and $Y_e$ are not representable from the 19
isotopes we carry in the main network. For this reason, when we are
using the NSE network, we always take the composition quantities in
the EOS directly from the auxiliary state in each zone instead of
using the $X_k$ directly. Our equation of state needs $\bar{Z}$ in addition
to the auxiliary quantities, which is is easily computed as
\MarginPar{might be worth spelling out exactly what inputs the NSE EOS needs to make things crystal clear}
\begin{equation}
\bar{Z} = \bar{A} Y_e
\end{equation}

@@

We initialize the mass fractions, $X_k$, and then compute the
electron fraction, $Y_e$, using (\ref{eq:aux:ye}).
For the two other composition
quantities we carry, $\bar{A}$, and $(B/A)$, we need values that are
consistent with the value of $Y_e$ and the nuclei stored in the NSE
table.  Therefore, if the thermodynamic conditions put us in NSE
(using the conditions defined below), then we obtain $\bar{A}$ and
$(B/A)$ from the NSE table.  Otherwise, we compute these directly from
$X_k$ using (\ref{eq:aux:abar}) and (\ref{eq:aux:bea}).
